A hierarchical failure-time model for observational data exhibiting infant-mortality and wearout failure modes

### 2017-10-31 paper/aosgflp.tex
Final round of edits.

The reliability of many engineered products follows a similar pattern. Relatively high rates of failure occurring early (``infant mortality'') is due to manufacturing defects.  After this ``burn-in'' period, failure rates stabilize after the majority of defective units have failed and are no longer in the population.  Finally, after prolonged use, rates of failure increase due to wearout.  Ignoring this pattern in failure rates can lead to spurious inferences about a product's reliability and suboptimal decisions. This highlights the importance of choosing a sufficiently flexible model.

@@

Often no information is available to identify why a unit failed, even when the failed units are available. Physical failure mode analysis (sometimes referred to as ``autopsy'') can be extremely time consuming and expensive. This presents a dilemma for analysts: the data may indicate multiple failure modes, contraindicating the use of a unimodal parametric distribution. However, without any knowledge of cause of failure, traditional competing risk models are not identifiable. \citet{chan} proposed the Generalized Limited Failure Population (GLFP) model. This model can provide a solution to the problem of unknown cause of failure (masking) in the special case where there is evidence of two modes of failure which impact different stages of product life. It avoids non-identifiability by introducing a parameter representing the population proportion defective. When this parameter is zero, the GLFP model reduces to a unimodal distribution. \\

The GLFP model has a meaningful parameterization and accommodates lifetime data with both infant mortality and wearout.  Unfortunately, it can require a lot of data to fit due to the model's complexity. When multiple sources of information are available, partial pooling, accomplished via hierarchical modeling, can reduce the amount of data required to produce stable parameter estimates. When multiple populations are of interest, comparisons based on separate, unrestricted GLFP model fits will be limited to those products with sufficient data. As we will show, hierarchical modeling of the GLFP parameters allows for borrowing of information across populations which imposes ``soft'' constraints on model parameters. This enables estimation of the lifetime distribution for all populations via shrinkage toward a ``pooled" model, with the degree of shrinkage inversely related to the amount of population specific information. We demonstrate computation of various quantities of interest while comparing reliability across populations using numerical integration over the posterior distribution with samples obtained via  Markov Chain Monte Carlo.

The structure of the paper is as follows. Section~\ref{sec:Background} introduces the proposed method and potential applications and examines previous related work.  Section~\ref{sec:GLFP model} introduces the GLFP model and illustrates its use with a subset of hard drive failure data from the company, Backblaze.  In Section~\ref{sec:Data}, we describe the complete Backblaze Hard Drive data set, which is used throughout as a motivating example. In Section~\ref{sec:Hierarchical GLFP model} we discuss using hierarchical modeling of the GLFP model parameters to extend the GLFP model to multiple populations. Section~\ref{sec:Data analysis} applies the hierarchical GLFP model to the hard disk drive data. First, we do model selection among four models of increasing complexity, using approximate leave-one-out cross-validation. Next, for the selected model, we assess the model fit using a graphical comparison of replicated data sets generated from the posterior distribution to the observed data. Finally, we present an evaluative comparison of populations taking into account practical considerations related to product lifetime. Section~\ref{sec:Discussion} describes potential applications of our model and consider limitation for inference implied by the model assumptions.

@@

\subsection{Weibull parameterization}
\label{sec:Weibull parameterization}
The Weibull cumulative
 distribution function (cdf) is
\begin{align}
\label{equation:weibull.cdf}
\Pr(T \leq t|\alpha,\beta ) &= F(t|\alpha,\beta)=1-
\exp \left [-\left (\frac{t}{\alpha} \right )^{\beta}
\right ], \quad t > 0,
\end{align}
where $\beta>0$ is the Weibull shape parameter and $\alpha>0$ is a
scale parameter. Because $\log(T)$ has a smallest extreme value
distribution (a member of the location-scale family of
distributions), the Weibull cdf can also be written as
\begin{align*}
\Pr(T \leq t| \mu,\sigma ) &= F(t| \mu,\sigma)= \Phi_{SEV}\left[\frac{\log(t)-\mu}{\sigma}\right], \quad t > 0,
\end{align*}
where $\Phi_{SEV}(z)=1-\exp[-\exp(z)]$ is the standard smallest extreme value
distribution cdf and
$\mu=\log(\alpha)$ and $\sigma=1/\beta$ are, respectively, location
and scale parameters for the distribution of $\log(T)$. Thus the Weibull
distribution is a member of the log-location-scale family of
distributions.

We will use an alternative parameterization
where $\alpha$ is replaced by the $p$ quantile $t_{p}=\alpha \left
[-\log(1-p)\right ]^{\sigma}$. Replacing $\alpha$ in (1) with the
$\alpha=t_{p}/[-\log(1-p)]^{\sigma}$ gives
\begin{align*}
\nonumber
\Pr(T \leq t|t_{p},\sigma ) = F(t|t_{p},\sigma)&=1-
\exp \left [-\left (\frac{t}{t_{p}/[-\log(1-p)]^{\sigma}} \right )^{1/ \sigma}
\right ]\\
\label{equation:reparameterized.weibull.cdf}
&=1 - \exp\left[\log(1-p)\left(\frac{t}{t_{p}}\right)^{1/\sigma}\right], \quad t > 0.
\end{align*}
There are two important reasons for using this parameterization.
\begin{itemize}
\item
Especially with a high-reliability product, it will be easier to
elicit prior information about a quantile  ($t_p$) in the lower tail of the
distribution than it will be to elicit prior information about
$\alpha$. There is, however, generally available
information the shape parameter $\sigma$ for a given failure
mechanism (e.g., if the failure is due to a wearout mechanism, then
it is known that $\sigma<1$). 
\item
Because of heavy censoring in reliability field data, the parameter
estimates of the $\mu$ and $\sigma$ parameters will generally be
highly correlated and thus specification of independent marginal
prior distributions would be be inappropriate. On the other hand,
estimates of $t_{p}$ and $\sigma$, for some appropriately chosen
value of $p$, will be approximately independent, allowing the easier
elicitation and specification of independent marginal prior
distributions. For example, if a typical field data set has 10\%
failing, then choosing $t_{0.05}$ would 
work well.
\end{itemize}

@@

The GLFP model can be understood as a mixture model with a binary latent variable, $\delta_i\ind \op{Bernoulli}(\pi)$. $\delta_i$ is an indicator for whether or not a unit $i$ is defective. Expressed conditional on~$\delta_i$,
\begin{align*}
P(T\le t | \delta_i=1) =& 1 -(1-F_1(t))(1-F_2(t))\\
P(T\le t | \delta_i=0) =& F_2(t).
\end{align*}

@@

\subsubsection{Likelihood}
We now give the general form for the likelihood function, taking into account left truncation and right censoring.  Let $t_{i}$ denote the end of the observed lifetime of unit $i$, in hours.  Let $t_i^L$ be the left truncation time, the age of unit $i$ when data reporting commenced. Additionally, let $c_i$ be an indicator for censoring; $c_i=1$ if the failure time is right-censored, $c_1=0$ if the unit failed (at time $t_i$). The likelihood for the GLFP is a function of the parameter $\bm{\theta} = (\pi,t_{p1}, \sigma_1, t_{p2}, \sigma_2)$.  Assuming the lifetimes of all units are independent, the likelihood for the data, $t_1,\ldots,t_n$ is given by
\begin{equation*}
L(\bm{\theta})= \prod_{i=1}^{n} \left[\frac{h(t_i;\bm{\theta})}{1-H(t_i^L;\bm{\theta})}\right]^{1-c_i} \left[ \frac{1-H(t_i;\bm{\theta})}{1-H(t_i^L;\bm{\theta})} \right]^{c_i}
\end{equation*}

\section{Motivating Example}
\label{sec:Data}
\subsection{Backblaze hard drive data}
Backblaze is a company that offers cloud backup storage to protect against data loss.  Since 2013 it has been collecting data on hard drives operating at its facility.  The purpose is to provide consumers and businesses with reliability information on different hard drive-models.  The hard drives continuously spin in controlled storage pods.  Drives are run until failure.  When a hard drive fails it is removed and replaced.  In addition, the number of storage pods is increasing as Backblaze adds drives to its storage capacity.  Every quarter Backblaze makes its hard drive data publicly available through their website (\url{https://www.backblaze.com/b2/hard-drive-test-data.html}, Accessed April 1, 2016)\nocite{backblaze}. In addition, Backblaze publishes summary statistics of the different hard drive-models currently operating.  No other analysis or modeling of the failure data is provided.  Backblaze does, however, encourage others to further analyze their data.

As of the first quarter of 2016, Backblaze was collecting and reporting data on 63 different drive-models.  Some drive-models have been running since 2013 or before, while others were added at a later date.  Data have been reported on 75,297 different hard drives that are or where in operation.  The number of drives varies by drive-model; some drive-models have only have a service record for a single drive whereas the maximum number of daily service records for a single drive-model is 35,860.  Figure 1 shows a scatterplot of the total observed running time in hundred of thousands hours versus the total number of failures for drive-models with at least 3 failures.  For model identification, a minimum of three failures was the criterion for hard drive brands to be included in our analysis.

@@

\subsection{Analysis of a single drive-model}
\label{subsec:ex1}
To illustrate the GLFP model, we will present an analysis of the drive-model with the most observed failures, Drive-model 14.  The Kaplan-Meier (K-M) estimate plotted below suggests at least two failure modes.  The curve has a slow ramp up in failures till about 10,000 hours (early failures), increases more rapidly from about 10,000 to 20,000 hours (presumably wearout failures).  In addition, computer hard drives are known to have a mixture of early and late failures \citep{chan}.  Therefore, there is both an empirical and a theoretical justification to apply the GLFP model.

@@

Probability plotting is a simple method to assess and compare the adequacy of members of the log-location-scale families of distributions.  After properly transforming the axes of a plot, graphing an empirical estimate of fraction failing as a function of time along with pointwise confidence bands provides a visual check for distributional goodness of fit.  We applied this method using the Kaplan-Meier nonparametric estimate of the empirical cdf.  With left truncation, however, the standard Kaplan-Meier estimator is biased, so we used an adjusted version due to \citet[Chapter 11]{meeker} (see Appendix for a detailed description).

@@

As discussed in Section \ref{sec:Weibull parameterization}, we reparameterize the Weibull distribution in terms of a quantile and the shape parameter because the data we encounter are more informative about the lower tail of their respective lifetime distribution (note that if $T$ has a Weibull distribution, $\sigma$ is a shape parameter for the distribution of $T$ and a scale parameter for the distribution of $\log(T)$). We truncate the distribution of $\sigma_{2g}$ at $1$ (indicated by $T(0,1)$ above) restricting the wearout failure mode to have an increasing hazard function (e.g., $\beta_{2g} = 1/\sigma_{2g}>1$). %We choose to model these parameters with log-normal and logit-normal distributions because many populations require strong regularization which the normal, with its exponentially decreasing tails, provides.

@@

For all of the models we consider, the parameters for the infant mortality failure mode are held in common across drive-models.  We found that there was often insufficient information to model these parameters hierarchically.  Moreover, assuming a common distribution for infant mortality provides a meaningful interpretation and comparison of $\pi_g$ and $\pi_{g'}$ ($g \neq g'$). Also the failure-time distribution of the defective subpopulation is not of high interest (as opposed to the proportion defective.)

\subsubsection{Prior distributions}
\label{sec:Prior distributions}
To complete the full probability model, we need to select prior distributions for the parameters governing the hierarchical model. We select proper prior distributions to ensure a proper posterior distributions.

@@

Figure \ref{fig:fig2} provides a visual comparison for Models 1 through 4 by plotting the pointwise posterior median of the cdf for each drive-model.  To make the plot comparable, we use an adjustment based on a parametric model (Model 4). The large left panel shows the adjusted K-M estimate of the same. The adjusted K-M estimates on the right side of Figure \ref{fig:fig2} shows that the set of estimated failure curves for all four models that we fit. The smaller plots correspond to Models 1 through 4.  Note that while all the paths for the posterior estimates necessarily pass through the origin, the K-M estimates do not, because, for the K-M estimator, inference is entirely conditional on survival up to left-most left-trunctation time.

%Should we be brief discussing the plot?
These plots suggest that Model 1 is insufficient to explain the observed data. Model 2 certainly captures more of the heterogeneity observed in the K-M estimates; we observe that the assumption of a common $\sigma_2(=\sigma_{2,g})$ results in a very similar progressions in cdf, which may be too restrictive. Model 3, which removes this restriction on $\sigma_{2,g}$ suggests that there is evidence to support variation in this parameter among drive-models. While Model 3 and 4 do display differences, they are relatively subtle.

@@

Drive-model 9 shows a high proportion of  of early failures, a fact which Model 1 fails to capture. Model 2 addresses this by estimating an earlier time to wearout, but still results in a poor fit to the data. Models 3 and 4 conform more closely to the adjusted K-M estimate. The disagreement between Models 3 and 4 for Drive-model 9, is interesting: Model 4 allows the proportion of defective units to vary by drive-model, but Model 3 appears to fit just as well in this case, by increasing the scale parameter for the wearout failure mode.

@@

While MTTF is often an important metric, due to the
anticipation of advancements in technology, we can expect that the
relative value of computer hardware will depreciate rather quickly. In simple terms, given two hard drives, one would prefer to have both of them work for five years than for one to work for ten years and the other to not work at all. To account
for depreciation, rather than using MTTF as the metric for Drive-model comparison, we use the value at replacement. The US Internal Revenue Service considers
computer hardware to be ``5-year'' equipment \citep{f4562}. Using``the declining
balance method'' the rate of depreciation is 40\% per year.

@@

Posterior credible intervals for $L(t_{g,new})$ are shown in the left panel of Figure \ref{fig5}. A zoomed version of the top eight drive-models, as ranked by $\op{E}(L(t_{g,new})|y)$ are shown in the bottom right panel. The panel above shows credible intervals for MTTF. We can see that ranking by MTTF would lead to a different result -- a new Drive-model 8 unit is expected to last the longest, but the possibility of it failing early is higher than for the drive-models ranked highest by our depreciation-aware metric. The top four drive-models (4, 5, 2, 3) seem comparable, with a new Drive-model 4 unit expected to depreciate the most. However, given the discrepancy of the model fit for Drive-model 4, noted in the previous subsection, in the absence of more early life data, we might harbor some lingering concern about possible quality-control issues with this Drive-model.

@@

\section{Discussion}
\label{sec:Discussion}
This paper offers a new approach to modeling and making inference for the lifetime of consumer products using incomplete field reliability data.  Products with long lifetimes often have few failures and when failures do occur the cause is frequently unknown to the analyst.  The GLFP model provides a framework to accurately model data with evidence of multiple failure modes. Moreover, when there are multiple product populations within the same product class, our hierarchical modeling approach borrows strength across brands with many observed failures to help make inference for those populations with little information.  This can be important when trying to leverage multiple sources of data with various sample sizes and levels of censoring and truncation.  We found that the use of weakly informative priors on the hyperparameters can increase the overall efficiency of the MCMC. %This makes standard parametric lifetime models inaccurate and difficult to estimate using classical estimation techniques such as ML.

We now address some important model assumptions and their potential for impacting statistical inference.

@@

Second, we assume exchangability of units within a population. This assumption is due in part to ignorance about which units are defective but also of potentially important covariates. We do not account for batch effects or varying conditions in the facility which have impacted the observed failure rates. These factors are confounded with Drive-model in our analysis. An example of a possible batch effect is noted in Section \ref{model-assessment} and illustrated by Figure \ref{fig:ex-mod-4}.

>>>>

The reliability of many engineered products follows a similar pattern. Relatively high rates of failure occurring early (``infant mortality'') is due to manufacturing defects.  After this ``burn-in'' period, failure rates stabilize after the majority of defective units have failed.  Finally, after prolonged use, rates of failure increase due to wearout.  Ignoring this pattern in failure rates can lead to spurious inferences about a product's reliability and suboptimal decisions. This highlights the importance of choosing a sufficiently flexible model.

@@

Often no information is available to identify why a unit failed, even when the failed units are available. Physical failure mode analysis (sometimes referred to as ``autopsy'') can be extremely time consuming and expensive. This presents a dilemma for analysts: the data may indicate multiple failure modes, contraindicating the use of a unimodal parametric distribution. However, without any knowledge of cause of failure, traditional competing risk models are not identifiable. \citet{chan} proposed the Generalized Limited Failure Population (GLFP) model. This model can provide a solution to the problem of unknown cause of failure in the special case where there is evidence of two modes of failure which impact different stages of product life. It avoids non-identifiability by introducing a parameter representing the population proportion defective. When this parameter is zero, the GLFP model reduces to a unimodal distribution. \\

The GLFP model has a meaningful parameterization and accommodates lifetime data with both infant mortality and wearout.  Unfortunately, it can require a lot of data to fit due to the model's complexity. When multiple sources of information are available, partial pooling, accomplished via hierarchical modeling, can reduce the amount of data required to produce stable parameter estimates. When multiple populations are of interest, comparisons based on separate, unrestricted GLFP model fits will be limited to those products with sufficient data. As we will show, hierarchical modeling of the GLFP parameters allows for borrowing of information across populations which imposes ``soft'' constraints on model parameters. This enables estimation of the lifetime distribution for all populations via shrinkage toward a ``pooled" model, with the degree of shrinkage inversely related to the amount of population specific information. We demonstrate computation of various quantities of interest while comparing reliability across populations using numerical integration over the posterior distribution with samples obtained via Markov Chain Monte Carlo (MCMC).

The structure of the paper is as follows. Section~\ref{sec:Background} introduces the proposed method and potential applications and examines previous related work.  Section~\ref{sec:GLFP model} introduces the GLFP model and illustrates its use with a subset of hard drive failure data from the company, Backblaze.  In Section~\ref{sec:Data}, we describe the complete Backblaze Hard Drive data set, which is used throughout as a motivating example. In Section~\ref{sec:Hierarchical GLFP model} we discuss using hierarchical modeling of the GLFP model parameters to extend the GLFP model to multiple populations. Section~\ref{sec:Data analysis} applies the hierarchical GLFP model to the hard drive data. First, we do model selection among four models of increasing complexity, using approximate leave-one-out cross-validation. Next, for the selected model, we assess the model fit using a graphical comparison of replicated data sets generated from the posterior distribution to the observed data. Finally, we present an evaluative comparison of populations taking into account practical considerations related to product lifetime. Section~\ref{sec:Discussion} describes potential applications of our model and limitations for inference implied by the model assumptions.

@@

\subsection{Weibull parameterization}
\label{sec:Weibull parameterization}
The Weibull cumulative
 distribution function (cdf) is
\begin{align}
\label{equation:weibull.cdf}
\Pr(T \leq t|\alpha,\beta ) &= F(t|\alpha,\beta)=1-
\exp \left [-\left (\frac{t}{\alpha} \right )^{\beta}
\right ], \quad t > 0,
\end{align}
where $\beta>0$ is the Weibull shape parameter and $\alpha>0$ is a
scale parameter. Because $\log(T)$ has a smallest extreme value
distribution (a member of the location-scale family of
distributions), the Weibull cdf can also be written as
\begin{align*}
\Pr(T \leq t| \mu,\sigma ) &= F(t| \mu,\sigma)= \Phi_{SEV}\left[\frac{\log(t)-\mu}{\sigma}\right], \quad t > 0,
\end{align*}
where $\Phi_{SEV}(z)=1-\exp[-\exp(z)]$ is the standard smallest extreme value
distribution cdf and
$\mu=\log(\alpha)$ and $\sigma=1/\beta$ are, respectively, location
and scale parameters for the distribution of $\log(T)$. Therefore, the Weibull
distribution is a member of the log-location-scale family of
distributions.

We will use an alternative parameterization
where $\alpha$ is replaced by the $p$ quantile $t_{p}=\alpha \left
[-\log(1-p)\right ]^{\sigma}$. Replacing $\alpha$ in (1) with the
$\alpha=t_{p}/[-\log(1-p)]^{\sigma}$ gives
\begin{align*}
\nonumber
\Pr(T \leq t|t_{p},\sigma ) = F(t|t_{p},\sigma)&=1-
\exp \left [-\left (\frac{t}{t_{p}/[-\log(1-p)]^{\sigma}} \right )^{1/ \sigma}
\right ]\\
\label{equation:reparameterized.weibull.cdf}
&=1 - \exp\left[\log(1-p)\left(\frac{t}{t_{p}}\right)^{1/\sigma}\right], \quad t > 0.
\end{align*}
There are two important reasons for using this parameterization.
\begin{itemize}
\item
Especially with a high-reliability product, it will be easier to
elicit prior information about a quantile  ($t_p$) in the lower tail of the
distribution than it will be to elicit prior information about
$\alpha$. In addition, there is generally available
information about the shape parameter, $\sigma$, for a given failure
mechanism (e.g., if the failure is due to a wearout mechanism, then
it is known that $\sigma<1$). 
\item
Because of heavy censoring in reliability field data, the parameter
estimates of the $\mu$ and $\sigma$ parameters will generally be
highly correlated and thus specification of independent marginal
prior distributions would be be inappropriate. On the other hand,
estimates of $t_{p}$ and $\sigma$, for some appropriately chosen
value of $p$, will be approximately independent, allowing the easier
elicitation and specification of independent marginal prior
distributions. For example, if a typical field data set has 10\% of units
failing, then choosing $t_{0.05}$ would 
work well.
\end{itemize}

@@

The GLFP model can be understood as a mixture model with a binary latent variable, $\delta_i\ind \op{Bernoulli}(\pi)$. $\delta_i$ is an indicator for whether or not unit $i$ is defective. Expressed conditional on~$\delta_i$,
\begin{align*}
P(T\le t | \delta_i=1) =& 1 -(1-F_1(t))(1-F_2(t))\\
P(T\le t | \delta_i=0) =& F_2(t).
\end{align*}

@@

\subsubsection{Likelihood}
We now give the general form for the likelihood function, taking into account left truncation and right censoring.  Let $t_{i}$ denote the end of the observed lifetime of unit $i$, in hours.  Let $t_i^L$ be the left truncation time, the age of unit $i$ when data reporting commenced. Additionally, let $c_i$ be an indicator for censoring; $c_i=1$ if the failure time is right-censored, $c_1=0$ if the unit failed (at time $t_i$). The likelihood for the GLFP is a function of the parameter $\bm{\theta} = (\pi,t_{p1}, \sigma_1, t_{p2}, \sigma_2)$.  Assuming the lifetimes of all units are independent, the likelihood for the data, $t_1,\ldots,t_n$ is
\begin{equation*}
L(\bm{\theta})= \prod_{i=1}^{n} \left[\frac{h(t_i;\bm{\theta})}{1-H(t_i^L;\bm{\theta})}\right]^{1-c_i} \left[ \frac{1-H(t_i;\bm{\theta})}{1-H(t_i^L;\bm{\theta})} \right]^{c_i}
\end{equation*}

\section{Motivating Example}
\label{sec:Data}
\subsection{Backblaze hard drive data}
Backblaze is a company that offers cloud backup storage to protect against data loss.  Since 2013 it has been collecting data on hard drives operating at its facility.  The purpose is to provide consumers and businesses with reliability information on different hard drive-models.  The hard drives continuously spin in controlled storage pods.  Drives are run until failure.  When a hard drive fails it is removed and replaced.  In addition, the number of storage pods is increasing as Backblaze adds drives to its storage capacity.  Every quarter Backblaze makes its hard drive data publicly available through their website (\url{https://www.backblaze.com/b2/hard-drive-test-data.html}, Accessed April 1, 2016)\nocite{backblaze}. In addition, Backblaze publishes summary statistics of the different drive-models currently operating.  No other analysis or modeling of the failure data is provided.  Backblaze does, however, encourage others to further analyze their data.

As of the first quarter of 2016, Backblaze was collecting and reporting data on 63 different drive-models.  Some drive-models have been running since 2013 or before, while others were added at a later date.  Data have been reported on 75,297 different hard drives that are or were in operation.  The number of drives varies by drive-model; some drive-models only have a service record for a single drive whereas the maximum number of daily service records for a single drive-model is 35,860.  Figure 1 shows a scatterplot of the total observed running time in hundred of thousands hours versus the total number of failures for drive-models with at least 3 failures.  For model identification, a minimum of three failures was the criterion for hard drive brands to be included in our analysis.

@@

\subsection{Analysis of a single drive-model}
\label{subsec:ex1}
To illustrate the GLFP model, we will present an analysis of the drive-model with the most observed failures, Drive-model 14.  The Kaplan-Meier (K-M) estimate plotted below suggests at least two failure modes.  The curve has a slow ramp up in failures till about 10,000 hours (early failures), and increases more rapidly from about 10,000 to 20,000 hours (presumably wearout failures).  In addition, computer hard drives are known to have a mixture of early and late failures \citep{chan}.  Therefore, there is both an empirical and a theoretical justification to apply the GLFP model.

@@

Probability plotting is a simple method to assess and compare the adequacy of members of the log-location-scale family of distributions.  After properly transforming the axes of a plot, graphing an empirical estimate of fraction failing as a function of time along with pointwise confidence bands provides a visual check for distributional goodness of fit.  We applied this method using the Kaplan-Meier nonparametric estimate of the empirical cdf.  With left truncation, however, the standard Kaplan-Meier estimator is biased, so we used an adjusted version due to \citet[Chapter 11]{meeker} (see Appendix for a detailed description).

@@

As discussed in Section \ref{sec:Weibull parameterization}, we reparameterize the Weibull distribution in terms of a quantile and the shape parameter because the data we encounter are more informative about the lower tail of their respective lifetime distribution (note that if $T$ has a Weibull distribution, $\sigma$ is a shape parameter for the distribution of $T$ and a scale parameter for the distribution of $\log(T)$). We truncate the distribution of $\sigma_{2g}$ at $1$ (indicated by $T(0,1)$ above) restricting the wearout failure mode to have an increasing hazard function (i.e., $\beta_{2g} = 1/\sigma_{2g}>1$). %We choose to model these parameters with log-normal and logit-normal distributions because many populations require strong regularization which the normal, with its exponentially decreasing tails, provides.

@@

For all of the models we consider, the parameters for the infant mortality failure mode are held in common across drive-models.  We found that there was often insufficient information to model these parameters hierarchically.  Moreover, assuming a common distribution for infant mortality provides a meaningful interpretation and comparison of $\pi_g$ and $\pi_{g'}$ ($g \neq g'$). Also the failure-time distribution of the defective subpopulation (as opposed to the proportion defective) is not of high interest.

\subsubsection{Prior distributions}
\label{sec:Prior distributions}
To complete the full probability model, we need to select prior distributions for the parameters governing the hierarchical model. We select proper prior distributions to ensure proper posterior distributions.

@@

Figure \ref{fig:fig2} provides a visual comparison for Models 1 through 4 by plotting the pointwise posterior median of the cdf for each drive-model.  The large left panel shows the adjusted K-M estimate.  The smaller plots correspond to Models 1 through 4.  To make the plots comparable, we use an adjustment based on the parametric model (Model 4).  Note that while all the paths for the posterior estimates necessarily pass through the origin, the K-M estimates do not, because, for the K-M estimator, inference is entirely conditional on survival up to left-most left-trunctation time.

%Should we be brief discussing the plot?
These plots suggest that Model 1 is insufficient to explain the observed data. Model 2 certainly captures more of the heterogeneity observed in the K-M estimates; we observe that the assumption of a common $\sigma_2$ results in very similar progressions in the cdf, which may be too restrictive. Model 3, which allows $\sigma_2$ to vary by group, suggests there is evidence to support variation in this parameter among drive-models. While Model 3 and 4 do display differences, they are relatively subtle.

@@

Drive-model 9 shows a high proportion of early failures, a fact which Model 1 fails to capture. Model 2 addresses this by estimating an earlier time to wearout, but still results in a poor fit to the data. Models 3 and 4 conform more closely to the adjusted K-M estimate. The disagreement between Models 3 and 4 for Drive-model 9, is interesting: Model 4 allows the proportion of defective units to vary by drive-model, but Model 3 appears to fit just as well in this case, by increasing the scale parameter for the wearout failure mode.

@@

While MTTF is often an important metric, due to the
anticipation of advancements in technology, we can expect that the
relative value of computer hardware will depreciate rather quickly. In simple terms, given two hard drives, one would prefer to have both of them work for five years than for one to work for ten years and the other to not work at all. To account
for depreciation, rather than using MTTF as the metric for drive-model comparison, we use the value at replacement. The US Internal Revenue Service considers
computer hardware to be ``5-year'' equipment \citep{f4562}. Using``the declining
balance method'' the rate of depreciation is 40\% per year.

@@

Posterior credible intervals for $L(t_{g,new})$ are shown in the left panel of Figure \ref{fig5}. A zoomed version of the top eight drive-models, as ranked by $\op{E}(L(t_{g,new})|y)$ are shown in the bottom right panel. The panel above shows credible intervals for MTTF. We can see that ranking by MTTF would lead to a different result -- a new Drive-model 8 unit is expected to last the longest, but the possibility of it failing early is higher than for the drive-models ranked highest by our depreciation-aware metric. The top four drive-models (4, 5, 2, 3) seem comparable, with a new Drive-model 4 unit expected to depreciate the most. However, given the discrepancy of the model fit for Drive-model 4 (noted in the previous subsection), in the absence of more early life data, we might harbor some lingering concern about possible quality-control issues with this Drive-model.

@@

\section{Discussion}
\label{sec:Discussion}
This paper offers a new approach to modeling and making inference for the lifetime of consumer products using incomplete field reliability data.  Products with long lifetimes often have few failures and when failures do occur the cause is frequently unknown to the analyst.  The GLFP model provides a framework to accurately model data with evidence of multiple failure modes. Moreover, when there are multiple product populations within the same product class, our hierarchical modeling approach borrows strength across brands with many observed failures to help make inference for those populations with little information.  This can be important when trying to leverage multiple sources of data with various sample sizes and levels of censoring and truncation.  We found that the use of weakly informative priors on the hyperparameters can increase the overall efficiency of the MCMC.  We now address some important model assumptions and their potential for impacting statistical inference.

@@

Second, we assume exchangability of units within a population. This assumption is due in part to ignorance about which units are defective but also of potentially important covariates. We do not account for batch effects or varying conditions in the facility which have impacted the observed failure rates. These factors are confounded with drive-model in our analysis. An example of a possible batch effect is noted in Section \ref{model-assessment} and illustrated by Figure \ref{fig:ex-mod-4}.
